
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


# Loading packages

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(agricolae)
library(ggjoy)
library(drc)
library(ggpubr)
library(rstatix)
library(ec50estimator)
library(car)
library(FactoMineR)
library(factoextra)

```


## Mycelium growth rate

```{r}

mgr <- read_excel("data/lab_experiment.xlsx", sheet = "mycelia") %>%
  group_by(isolate) %>% 
  mutate(rep1 = as.numeric(rep1),
          rep2 = as.numeric(rep2))

nrow(mgr)

```

### Change the format of the data

```{r}

mgr1 <- mgr %>% gather(rep, mg5, rep1:rep2)

head(mgr1)

```


### Mycelia growth rate by day

```{r}
  
mgr2 <- mgr1 %>%
  group_by(region, location, isolate, man_zone) %>%
  summarize(mean_mg = mean(mg5),
            mgr_day = mean_mg/5) 

```

### Data analysis - Mycelia growth

```{r message=FALSE, warning=FALSE}

mycelia.lm<-with(mgr2, lm(mgr_day~region)) 

summary(mycelia.lm)
anova(mycelia.lm)

cv.model(mycelia.lm)
LSD.test(mycelia.lm,"region",console=TRUE)

```


### Visualize the data - Mycelium growth

```{r}

mycelium_mlh <- mgr2 %>% 
  group_by(man_zone) %>%   
  ggplot(aes(x=man_zone, y=mgr_day)) +
   geom_boxplot(size = 1.1, width = 0.3) +
  geom_jitter(size = 2, alpha = 0.5, width = 0.2, color = "#E69F00") +
  scale_x_discrete(limits=c("North", "Central", "South")) +
  scale_color_manual(values=c("#E69F00"))+
   labs(y = "Radial growth rate (mm/day)", 
        x = "",
       title = "") +
  theme_minimal()+
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12))

mycelium_mlh

#ggsave("plots/mycelium_mhl.png", width = 7, height = 5, dpi = 300)

```

## Conidia production

```{r}

cnd <- read_excel("data/lab_experiment.xlsx", sheet = "conidia")

```


### Data analysis - Conidia production

```{r message=FALSE, warning=FALSE}

conidia.lm<-with(cnd, lm(conc_spores~region)) 

summary(conidia.lm)
anova(conidia.lm)

cv.model(conidia.lm)
LSD.test(conidia.lm,"region",console=TRUE)

```


### Visualize the data - Conidia production

```{r message=FALSE, warning=FALSE}

cnd_mlh <- cnd %>% 
  group_by(man_zone) %>% 
  ggplot(aes(x=man_zone, y=conc_spores)) +
   geom_boxplot(size = 1.1, width = 0.3, outlier.colour = NA) +
  geom_jitter(size = 2, alpha = 0.5, width = 0.2, color = "#56B4E9") +
  scale_x_discrete(limits=c("North", "Central", "South")) +
  scale_color_manual(values=c("#56B4E9")) +
  theme_minimal() +
   labs(y = expression(N.~of~macroconidia~x~10 ^ {3}),
        x = "",
       title = "",
       color = "",
       fill = "" ) +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12))

cnd_mlh

#ggsave("plots/cnd_mhl.png", width = 7, height = 5, dpi = 300)

```


## GRID

```{r}
library(cowplot)

grid <- plot_grid(mycelium_mlh, cnd_mlh, ncol = 2, align = "v", labels = c("A", "B"))

grid

ggsave("figures/Figure_03.png", width = 10, height = 4, dpi = 300)


```


## Fungicide sensitivity

```{r}

fung <- read_excel("data/lab_experiment.xlsx", sheet = "fungicide") %>%
  filter(isolate!="PH1")


```


### Change the format of the data

```{r}
fung1 <- fung %>%
  group_by(assay, fungicide, isolate, dose, rep) %>%
  summarize(mgr = c(da+db)/2)

```

### Data analysis - TEB

```{r message=FALSE, warning=FALSE}
## Checking the difference between assays

teb <- fung1 %>%
  filter(fungicide!="Metconazole")

teb_lm<-with(teb, lm(mgr~assay)) 

summary(teb_lm)
anova(teb_lm)

cv.model(teb_lm)
LSD.test(teb_lm,"assay",console=TRUE)

```

### Combining assays - TEB

```{r}
assay1 <- teb %>% 
  filter(assay==1)

assay2 <- teb %>% 
  filter(assay==2)

assay2$rep[assay2$rep==1]<-3
assay2$rep[assay2$rep==2]<-4
assay2$assay[assay2$assay==2]<-1

teb1 <- rbind(assay1, assay2) %>% 
  arrange(isolate, dose)

```



### Data analysis - MET

```{r message=FALSE, warning=FALSE}
## Checking the difference between assays

met <- fung1 %>%
  filter(fungicide!="Tebuconazole")

met_lm<-with(met, lm(mgr~assay)) 

summary(met_lm)
anova(met_lm)

cv.model(met_lm)
LSD.test(met_lm,"assay",console=TRUE)

```


### Combining assays - MET

```{r}

assay1_met <- met %>% 
  filter(assay==1)

assay2_met <- met %>% 
  filter(assay==2)

assay2_met$rep[assay2_met$rep==1]<-3
assay2_met$rep[assay2_met$rep==2]<-4
assay2_met$assay[assay2_met$assay==2]<-1

met1 <- rbind(assay1_met, assay2_met) %>% 
  arrange(isolate, dose)

```


### Combining TEB and MET dataset

```{r}

fung_all <- rbind(teb1, met1)

```


### EC50 estimation

```{r message=FALSE, warning=FALSE}

library(ec50estimator)
library(drc)

ec50 = estimate_EC50(mgr~dose,
                        data = fung_all,
                        isolate_col = "isolate", 
                        strata_col =  c("fungicide"),
                        interval = "delta",
                        fct = LL.4())

ec50 <- ec50 %>%
  rename(
    isolate = ID)

## Export data
#write.csv(ec50, file = "data/ec50_region.csv")

```


### Statistical analysis - TEB

```{r message=FALSE, warning=FALSE}

ec50_all <- read_csv("data/ec50_region.csv")


## Tebuconazole

ec50_teb <- ec50_all %>%
  filter(fungicide =="Tebuconazole")

ec50_teb %>%
  get_summary_stats(Estimate, type = "full")


## South 
teb_south <- ec50_teb %>%
  filter(region == "South") 

## Central
teb_central <- ec50_teb %>%
  filter(region == "Central")


## North
teb_north <- ec50_teb %>%
  filter(region == "North")



## Kolmogorov-Smornov test

#H0 = equal distribution
#H1 = different distributions

ks.test(teb_south$Estimate, teb_central$Estimate, alternative = "two.side")
ks.test(teb_south$Estimate, teb_north$Estimate, alternative = "two.side")
ks.test(teb_central$Estimate, teb_north$Estimate, alternative = "two.side")

```

## Statistical analysis - MET

```{r message=FALSE, warning=FALSE}
## Tebuconazole

ec50_met <- ec50_all %>%
  filter(fungicide =="Metconazole")

ec50_met %>%
  get_summary_stats(Estimate, type = "full")


## South 
met_south <- ec50_met %>%
  filter(region == "South") 

## Central
met_central <- ec50_met %>%
  filter(region == "Central")


## North
met_north <- ec50_met %>%
  filter(region == "North")



## Kolmogorov-Smornov test

#H0 = equal distribution
#H1 = different distributions

ks.test(met_south$Estimate, met_central$Estimate, alternative = "two.side")
ks.test(met_south$Estimate, met_north$Estimate, alternative = "two.side")
ks.test(met_central$Estimate, met_north$Estimate, alternative = "two.side")

```


## Data visualization - Fungicide sensitivity

```{r}

ec50_all %>% 
  ggplot(aes(x = Estimate, fungicide, y = fungicide, color = fungicide, point_color = fungicide, fill = fungicide)) +
  geom_density_ridges(
    jittered_points = TRUE,
    size = 0.5,
    width = 0.2, alpha = 0.5, scale = 0.9, position = "raincloud") +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  scale_color_manual(values = c("#00AFBB", "#E7B800"), guide = "none") +
  scale_discrete_manual("point_color", values = c("#00AFBB", "#E7B800"), guide = "none") +
  labs(x = expression("EC"[50]^{}*~"(mg/L)"),
                  y = "") +
  theme(legend.position = "none")+
  xlim (-0.06,1)
  

ggsave("figures/Figure_05.png", width = 7, height = 4, dpi = 300)

```

