
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Loading packages

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(easyanova)
library(agricolae)

```


## FHB severity (%)

```{r message=FALSE, warning=FALSE}

sev <- read_excel("data/field_experiment.xlsx", sheet = "FHB_sev")

```


### Summarize data

```{r}
sev1 <- sev %>%
  mutate(treat = as.character(treat),
          block = as.character(block)) %>% 
  group_by(location, block, treat, treat_code, rep) %>%
  summarize(sev = (spikelets_dis*100)/spikelets)

```


### Analyze by location - Rock Springs

```{r message=FALSE, warning=FALSE}

sev1_RS <- sev1 %>% 
   filter(location!="Manheim")

sev_rs.lm<-with(sev1_RS, lm(sev~treat_code+block)) 

summary(sev_rs.lm)
anova(sev_rs.lm)

cv.model(sev_rs.lm)
LSD.test(sev_rs.lm,"treat_code", console=TRUE)

```


### Analyze by location - Manheim

```{r message=FALSE, warning=FALSE}

sev1_MH <- sev1 %>% 
   filter(location!="Rock Springs")

sev_mh.lm<-with(sev1_MH, lm(sev~treat_code+block)) 

summary(sev_mh.lm)
anova(sev_mh.lm)

cv.model(sev_mh.lm)
LSD.test(sev_mh.lm,"treat_code", console=TRUE)

```


### Visualize the data - FHB severity (%)

```{r}

sev_mlh <- sev1 %>%  
  ggplot(aes(x = treat_code,
             y = sev,
             fill = location)) +
  geom_boxplot(size = 0.6,
               outlier.colour = NA, width=0.4,
               position = position_dodge(width = 0.5)
               ) +
  geom_jitter(position=position_jitterdodge(dodge.width=0.5, jitter.width = 0.1),
              size=1.7,
              alpha=0.6, 
              aes(colour=location)) +
   theme_minimal() +
  scale_color_manual(breaks = c("Manheim", "Rock Springs"), values=c("#00AFBB", "#E7B800")) +
  scale_fill_manual(breaks = c("Manheim", "Rock Springs"), values=c("white", "white")) +
  scale_x_discrete(limits=c("Check","North", "Central", "South"))+
  labs(y = "FHB severity (%)",
                      x = "", 
                      title = "",
      color = "", fill = "") +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12)) +
  #ylim(0,100)+
   theme(legend.title=element_blank()) +
   theme(legend.position = "none")+
   theme(legend.position = "top") 

sev_mlh

#ggsave("figures/FHB_sev.png", width = 7, height = 4, dpi = 300)

```



## Deoxynivalenol (DON)

```{r message=FALSE, warning=FALSE}

don <- read_excel("data/field_experiment.xlsx", sheet = "DON")

```


### Analyze by location - Rock Springs

```{r message=FALSE, warning=FALSE}

don_rs <- don %>% 
   filter(location!="Manheim")

don_rs.lm<-with(don_rs, lm(don~treat_code+block)) 

summary(don_rs.lm)
anova(don_rs.lm)

cv.model(don_rs.lm)
LSD.test(don_rs.lm,"treat_code", console=TRUE)

```


### Analyze by location - Manheim

```{r message=FALSE, warning=FALSE}

don_mh <- don %>% 
   filter(location!="Rock Springs")

don_mh.lm<-with(don_mh, lm(don~treat_code+block)) 

summary(don_mh.lm)
anova(don_mh.lm)

cv.model(don_mh.lm)
LSD.test(don_mh.lm,"treat_code", console=TRUE)
```


### Visualize the data - Deoxynivalenol (DON)

```{r}

don_mlh <- don %>%  
  ggplot(aes(x = treat_code,
             y = don,
             fill = location)) +
  geom_boxplot(size = 0.6,
               outlier.colour = NA, width=0.4,
               position = position_dodge(width = 0.5)
               ) +
  geom_jitter(position=position_jitterdodge(dodge.width=0.5, jitter.width = 0.1),
              size=1.7,
              alpha=0.6, 
              aes(colour=location)) +
   theme_minimal() +
  scale_color_manual(breaks = c("Manheim", "Rock Springs"), values=c("#00AFBB", "#E7B800")) +
  scale_fill_manual(breaks = c("Manheim", "Rock Springs"), values=c("white", "white")) +
   scale_x_discrete(limits=c("Check","North", "Central", "South"))+
  labs(y = "Deoxynivalenol (ppm)",
                      x = "", 
                      title = "",
      color = "", fill = "") +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12)) +
  #ylim(0,100)+
   theme(legend.title=element_blank()) +
   theme(legend.position = "none")+
   theme(legend.position = "top") 

don_mlh

#ggsave("plots/don_mlh.png", width = 7, height = 4, dpi = 300)

  
```


## Yield (kg/ha)

```{r message=FALSE, warning=FALSE}

yield <- read_excel("data/field_experiment.xlsx", sheet = "yield")

```


### Analyze by location - Rock Springs

```{r message=FALSE, warning=FALSE}

yld_rs <- yield %>% 
   filter(location!="Manheim")

yld_rs.lm<-with(yld_rs, lm(yield_kg~treat_code+block)) 

summary(yld_rs.lm)
anova(yld_rs.lm)

cv.model(yld_rs.lm)
LSD.test(yld_rs.lm,"treat_code", console=TRUE)

```


### Analyze by location - Manheim

```{r message=FALSE, warning=FALSE}

yld_lv <- yield %>% 
   filter(location!="Rock Springs")

yld_lv.lm<-with(yld_lv, lm(yield_kg~treat_code+block)) 

summary(yld_lv.lm)
anova(yld_lv.lm)

cv.model(yld_lv.lm)
LSD.test(yld_lv.lm,"treat_code", console=TRUE)
```

### Visualize the data - Yield

```{r}

yld_mlh <- yield %>%  
  ggplot(aes(x = treat_code,
             y = yield_kg,
             fill = location)) +
  geom_boxplot(size = 0.6,
               outlier.colour = NA, width=0.4,
               position = position_dodge(width = 0.5)
               ) +
  geom_jitter(position=position_jitterdodge(dodge.width=0.5, jitter.width = 0.1),
              size=1.7,
              alpha=0.6, 
              aes(colour=location)) +
   theme_minimal() +
  scale_color_manual(breaks = c("Manheim", "Rock Springs"), values=c("#00AFBB", "#E7B800")) +
  scale_fill_manual(breaks = c("Manheim", "Rock Springs"), values=c("white", "white")) +
   scale_x_discrete(limits=c("Check","North", "Central", "South"))+
  labs(y = "Yield (kg/ha)",
                      x = "", 
                      title = "",
      color = "", fill = "") +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12)) +
  #ylim(0,100)+
   theme(legend.title=element_blank()) +
   theme(legend.position = "none")+
   theme(legend.position = "top") 

yld_mlh

#ggsave("plots/yield_mlh.png", width = 7, height = 4, dpi = 300)

  
```


## Test Weight

```{r message=FALSE, warning=FALSE}

test_weight <- read_excel("data/field_experiment.xlsx", sheet = "yield")

```


### Analyze by location - Rock Springs

```{r message=FALSE, warning=FALSE}

tw_RS <- test_weight %>% 
   filter(location!="Manheim")

tw_RS.lm<-with(tw_RS, lm(tw_kg~treat_code+block)) 

summary(tw_RS.lm)
anova(tw_RS.lm)

cv.model(tw_RS.lm)
LSD.test(tw_RS.lm,"treat_code", console=TRUE)

```


### Analyze by location - Manheim

```{r message=FALSE, warning=FALSE}

tw_LD <- test_weight %>% 
   filter(location!="Rock Springs")

tw_LD.lm<-with(tw_LD, lm(tw_kg~treat_code+block)) 

summary(tw_LD.lm)
anova(tw_LD.lm)

cv.model(tw_LD.lm)
LSD.test(tw_LD.lm,"treat_code", console=TRUE)

```


### Visualize the data - Test weight

```{r}

tw_mlh <- test_weight %>%  
  ggplot(aes(x = treat_code,
             y = tw_kg,
             fill = location)) +
  geom_boxplot(size = 0.6,
               outlier.colour = NA, width=0.4,
               position = position_dodge(width = 0.5)
               ) +
  geom_jitter(position=position_jitterdodge(dodge.width=0.5, jitter.width = 0.1),
              size=1.7,
              alpha=0.6, 
              aes(colour=location)) +
   theme_minimal() +
  scale_color_manual(breaks = c("Manheim", "Rock Springs"), values=c("#00AFBB", "#E7B800")) +
  scale_fill_manual(breaks = c("Manheim", "Rock Springs"), values=c("white", "white")) +
   scale_x_discrete(limits=c("Check","North", "Central", "South"))+
   labs(y = expression(Test~weight~(kg~m^-3)),
        x = "",
       title = "",
       color = "",
       fill = "" ) +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12)) +
  #ylim(0,100)+
   theme(legend.title=element_blank()) +
   theme(legend.position = "none")+
   theme(legend.position = "top") 

tw_mlh

#ggsave("plots/tw_mlh.png", width = 7, height = 4, dpi = 300)

  
```


## Fusarium damage kernel (FDK)

```{r message=FALSE, warning=FALSE}

fdk <- read_excel("data/field_experiment.xlsx", sheet = "quality")

```


### Analyze by location - Rock Springs

```{r message=FALSE, warning=FALSE}

fdk_RS <- fdk %>% 
   filter(location!="Manheim")

fdk_RS.lm<-with(fdk_RS, lm(FDK~treat_code+block)) 

summary(fdk_RS.lm)
anova(fdk_RS.lm)

cv.model(fdk_RS.lm)
LSD.test(fdk_RS.lm,"treat_code", console=TRUE)

```

  

### Analyze by location - Manheim

```{r message=FALSE, warning=FALSE}

fdk_LD <- fdk %>% 
   filter(location!="Rock Springs")

fdk_LD.lm<-with(fdk_LD, lm(FDK~treat_code+block)) 

summary(fdk_LD.lm)
anova(fdk_LD.lm)

cv.model(fdk_LD.lm)
LSD.test(fdk_LD.lm,"treat_code", console=TRUE)

```
  

### Visualize the data - FDK

```{r}

fdk_mlh <- fdk %>%  
  ggplot(aes(x = treat_code,
             y = FDK,
             fill = location)) +
  geom_boxplot(size = 0.6,
               outlier.colour = NA, width=0.4,
               position = position_dodge(width = 0.5)
               ) +
  geom_jitter(position=position_jitterdodge(dodge.width=0.5, jitter.width = 0.1),
              size=1.7,
              alpha=0.6, 
              aes(colour=location)) +
   theme_minimal() +
  scale_color_manual(breaks = c("Manheim", "Rock Springs"), values=c("#00AFBB", "#E7B800")) +
  scale_fill_manual(breaks = c("Manheim", "Rock Springs"), values=c("white", "white")) +
   scale_x_discrete(limits=c("Check","North", "Central", "South"))+
   labs(y = "Fusarium-damaged kernels (%)",
        x = "",
       title = "",
       color = "",
       fill = "" ) +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12)) +
  #ylim(0,100)+
   theme(legend.title=element_blank()) +
   theme(legend.position = "none")+
   theme(legend.position = "top") 

fdk_mlh

#ggsave("plots/fdk_mlh.png", width = 7, height = 4, dpi = 300)

  
```


## Seed germination (%)

```{r message=FALSE, warning=FALSE}

germinability <- read_excel("data/field_experiment.xlsx", sheet = "germinability")

```



### Analyze by location - Rock Springs

```{r message=FALSE, warning=FALSE}

germ_RS <- germinability %>% 
   filter(location!="Manheim")

germ_RS.lm<-with(germ_RS, lm(perc~treat_code+block)) 

summary(germ_RS.lm)
anova(germ_RS.lm)

cv.model(germ_RS.lm)
LSD.test(germ_RS.lm,"treat_code", console=TRUE)

```


  Seed germination was not influenced by treatments in Rock Springs.


### Analyze by location - Manheim

```{r message=FALSE, warning=FALSE}

germ_LD <- germinability %>% 
   filter(location!="Rock Springs")

germ_LD.lm<-with(germ_LD, lm(perc~treat_code+block)) 

summary(germ_LD.lm)
anova(germ_LD.lm)

cv.model(germ_LD.lm)
LSD.test(germ_LD.lm,"treat_code", console=TRUE)

```


### Visualize the data - Seed germination (%)

```{r}

seed_mlh <- germinability %>%  
  ggplot(aes(x = treat_code,
             y = perc,
             fill = location)) +
  geom_boxplot(size = 0.6,
               outlier.colour = NA, width=0.4,
               position = position_dodge(width = 0.5)
               ) +
  geom_jitter(position=position_jitterdodge(dodge.width=0.5, jitter.width = 0.1),
              size=1.7,
              alpha=0.6, 
              aes(colour=location)) +
   theme_minimal() +
  scale_color_manual(breaks = c("Manheim", "Rock Springs"), values=c("#00AFBB", "#E7B800")) +
  scale_fill_manual(breaks = c("Manheim", "Rock Springs"), values=c("white", "white")) +
   scale_x_discrete(limits=c("Check","North", "Central", "South"))+
   labs(y = "Seed germination (%)",
        x = "",
       title = "",
       color = "",
       fill = "" ) +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size = 12)) +
   theme(legend.title=element_blank()) +
   theme(legend.position = "none")+
   theme(legend.position = "top") 

seed_mlh

#ggsave("plots/seed_ger_mlh.png", width = 7, height = 4, dpi = 300)

  
```

## GRID

```{r}
library(cowplot)

grid_mlh <- plot_grid(sev_mlh, don_mlh, yld_mlh, tw_mlh, fdk_mlh, seed_mlh,  ncol = 2, align = "h", labels = c("A", "B", "C", "D", "E", "F"))

grid_mlh

ggsave("figures/Figure_04.png", width = 10, height = 12, dpi = 300)


```
